State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-11 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changes to plots

\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta2.pdf}}

@@

\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/ZetaConvergence.pdf}}

@@

\begin{figure*}
	\begin{center}
\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=0.3\textwidth]{./Graph/ObservationFrequencyResponse.pdf}}
	\end{center}
	\caption{a:Field basis function frequency response (projected to a 1D plot because it is symmetric); b:Sensor frequency response (projected to a 1D plot because it is symmetric); c: The average FFT of the observed field.} 
\label{fig:FreqAnalysis} 
\end{figure*}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.

@@

\caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.}
\label{fig:KernelEstimates}
\end{figure*}
\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta1_ratio.pdf}}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/theta0_theta2_ratio.pdf}}\\
\caption{Distribution of the parameters ratios over 250 runs.}
\end{figure}
\label{fig:ParametersRatio}
\begin{figure}[th]
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
\subfigure[][]{\includegraphics[width=0.24\textwidth]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
\caption{The average FFT of the neural field; a: True field; b: Estimated field (showing the limited bandwidth).}
\label{fig:FFTTrueEstimate}
\end{figure}

  \begin{figure}
   	\begin{center}
   		\includegraphics[width=0.5\textwidth]{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The RMSE of the estimated field over time.} 
\label{fig:RMSE}
   \end{figure}

  \begin{figure}
   	\begin{center}
   		\includegraphics[width=0.5\textwidth]{./Graph/MAE.pdf} 
   	\end{center}
   	\caption{The mean of the absolute error over time, gray area shows $\pm$STD.} 
\label{fig:MAE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimationError90.pdf}}\\
\caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
\label{fig:FieldEstimate}
\end{figure*}

>>>>

\subfigure[][]{\includegraphics{./Graph/zeta.pdf}}
\subfigure[][]{\includegraphics{./Graph/theta0.pdf}}\\
\subfigure[][]{\includegraphics{./Graph/theta1.pdf}}
\subfigure[][]{\includegraphics{./Graph/theta2.pdf}}

@@

\subfigure[][]{\includegraphics[width=1.5in]{./Graph/ZetaConvergence.pdf}}

@@

\begin{figure*}
	\begin{center}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/BasisChar.pdf}}
\subfigure[][]{\includegraphics[scale=0.8]{./Graph/SensorChar.pdf}}
\subfigure[][]{\includegraphics[width=1.8in]{./Graph/ObservationFrequencyResponse.pdf}}\\
	\end{center}
	\caption{a:Field basis function frequency response (projected to a 1D plot because it is symmetric); b:Sensor frequency response (projected to a 1D plot because it is symmetric); c: The average FFT of the observed field.} 
\label{fig:FreqAnalysis} 
\end{figure*}
Following this, the distance between basis function, $\Delta_b$, was set to $2.5$ and the basis function width, $\sigma_{\phi}^2$, was set to 3.6, 3.16 mm full width at half maximum. Analysis said 3.9 from Parham's derivation, but 3.6 still overlaps and allows more high frequency details to be represented.

@@

\caption{Mean kernel estimates over 250 runs ;  true and estimated kernels are shown by solid
and dashed line respectively, the grey area shows 95\% confidence interval; Left: spatial domain; Right: frequency domain; a, b: wider basis functions; c,d: narrower basis functions.}
\label{fig:KernelEstimates}
\end{figure*}
\begin{figure}[th]
\subfigure[][]{\includegraphics{./Graph/theta0_theta1_ratio.pdf}}
\subfigure[][]{\includegraphics{./Graph/theta0_theta2_ratio.pdf}}\\
\caption{Distribution of the parameters ratios over 250 runs.}
\end{figure}
\label{fig:ParametersRatio}
\begin{figure}[th]
\centering
\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTTrueField.pdf}}\label{fig:FieldFFT}
\subfigure[][]{\includegraphics[scale=0.9]{./Graph/FFTEstimatedField.pdf}}\label{fig:EstimatedFieldFFT}\\
\caption{The average FFT of the neural field; a: True field; b: Estimated field (showing the limited bandwidth).}
\label{fig:FFTTrueEstimate}
\end{figure}

  \begin{figure}
   	\begin{center}
   		\includegraphics{./Graph/MRMSE.pdf} 
   	\end{center}
   	\caption{The mean of RMSE of the estimated field over 250 runs.} 
\label{fig:RMSE}
   \end{figure}
\begin{figure*}[!th]
\centering 
\subfigure[][]{\includegraphics[width=2in]{./Graph/TrueField90.pdf}}
\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimatedField90.pdf}}
\subfigure[][]{\includegraphics[width=2in]{./Graph/EstimationError90.pdf}}\\
\caption{One snapshot of the spatial field; a: True field; b: Estimated field; c: The absolute error.}
\label{fig:FieldEstimate}
\end{figure*}
